---
title: "An Example of Margin Figures"
author: "Erik"
subtitle: "Using the Quarto chunk option `column: margin`"
date: "2023-10-08"
---

# Introduction

Images and graphics play an integral role in Tufte’s work. To place figures in the margin you can use the **Quarto** chunk option `column: margin`. For example:

```{r}
#| label: fig-margin
#| fig-cap: "MPG vs horsepower, colored by transmission."
#| column: margin
#| message: false
library(ggplot2)
mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() + geom_smooth() +
  theme(legend.position = 'bottom')
```


Note the use of the `fig-cap` chunk option to provide a figure caption. You can adjust the proportions of figures using the `fig-width` and `fig-height` chunk options. These are specified in inches, and will be automatically scaled down to fit within the handout margin.

```{r}
#| label: fig-margin-second
#| fig-cap: "Icecream vs chocolate, colored by flavor."
#| fig-width: 20
#| column: margin
#| message: false
library(ggplot2)
mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() + geom_smooth() +
  theme(legend.position = 'bottom')
```
